---
title: "Prediction"
author: "K Hull"
date: "December 5, 2017"
output: html_document
---
#My Weightlifting Prediction is..

##Overview
Package caret provides a training function that can be used with Random Forest. caret will try several models and select a best model automatically. 

##Background
"Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large 
amount of data about personal activity relatively inexpensively. These type of devices are part of 
the quantified self movement - a group of enthusiasts who take measurements about themselves regularly
to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing 
that people regularly do is quantify how much of a particular activity they do, but they rarely quantify 
how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, 
arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways.
More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset)."

#conclusion 
I choose random forest method for conducting this project because it was more accurate based upon testing.

#Loading the Dataset
Below codes loaded the datasets and the necessary library.
```{r,echo=TRUE}
library(caret)
library(e1071)
library(lattice)
library(ggplot2)
library(randomForest)
library(rpart)
library(rpart.plot)
library(plyr)

set.seed(1234)
```
2a.`Exploring Data`


```{r,echo=TRUE}
'Data Loading and Cleaning'
# I have removed all the variables containing NA values.

#Download the dataset 
Training.D<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
Test.D<-  "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

#Load the dataset into memory, the function na.strings a character vector of strings which are to be interpreted as NA values
training <-  read.csv(url(Training.D),na.strings=c("NA","#DIV/0!",""))
testing <-  read.csv(url(Test.D),na.strings=c("NA","#DIV/0!",""))

training <-  training[, colSums(is.na(training)) == 0]
testing <- testing[, colSums(is.na(testing)) == 0]
```

`Cleaning the Data`
#view of columns with the removal of varibles that are not needed
```{r,echo=TRUE}
colnames(training[,c(1:7)])
training<- training[, -c(1:7)]
testing <- testing[, -c(1:7)]

# Identifiedthe columns and rows within the columns i elimated the varible names that are not directly related to the prdiction.The most abundant class is A, which is our target variable.

dim(testing)
dim(training )
table(training $classe)

```
` cross validation`
This technique is used to evaluate predictive models by partitioning the original sample into a training set to train the model, and a test set to evaluate it.
```{r,echo=TRUE}
set.seed(1234)
cv3 = trainControl(method="cv",number=3,allowParallel=TRUE,verboseIter=TRUE)
modrf = train(classe~., data=training, method="rf",trControl=cv3)
```
`Testing Data`
The subset the data from train to the dataset modtree
```{r,echo=TRUE}
modtree = train(classe~.,data=training,method="rpart",trControl=cv3)
```

`Evaluating the two model on the testing dataset`
```{r,echo=TRUE}
prf=predict(modrf,training)
ptree=predict(modtree,training)
table(prf,training$classe)
#Decision Tree Model
table(ptree,training$classe)
```
`Testing Dataset`
Now we will evaulate the prediction of the seleted test answer
```{r,echo=TRUE}
prf=predict(modrf,testing)
ptree=predict(modtree,testing)
table(prf,ptree)
```
Based on the dataset created and evaluated witht he help of the random forest model and the Tree model. I feel confident that the most accurate model for testing dataset in the random forest model
```{r,echo=TRUE}

answers=predict(modrf,testing)
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
answers
```



